---
title: "AIR exploration data"
author: "Bastiaan"
date: "2023-09-28"
output: html_document
---
```{r , load packages, echo=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyverse)
```

```{r echo=FALSE}
movies_with_air_condition <- read_csv("../../data/AIR_analysis/movies_with_air_condition.csv")
df <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos_endgame.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))
named_characters <- read_csv("../../data/AIR_analysis/filtered_named_characters.csv")
thanos <- read_csv("../../gen/data-preparation/output/thanos_endgame.csv")
```
# We started to do the anlysis midly. Here we just looked if there are more than 2 characters from the ethnicity. So they didn't neccesarly needed to be named. Moreover, the assigned ethnicities were based on two thresholds. 0.6 for a whole point and 0.25 for a halve a point. Here the scene index was 5 seconds for a new scene. T1 is from all the movies. Nevertheless, T2 and T3 are only from the movies which could be analysed. which were 1100. Moreover, we used people mentioned so there are most likely cases where someone is speaking about a person from the same ethncity group while they are actually not talking to that person. 

```{r echo=FALSE}
named_air_condit <- read_csv("../../gen/movies_with_air_condition_named.csv")
movies_simpson_named <- read_csv("../../gen/data-preparation/output/movies_simpson_named.csv")

df <- subset(df, imdb.com_imdbid %in% named_air_condit$tt_number)
movies_simpson_named <- subset(movies_simpson_named, Movie.ID %in% named_air_condit$tt_number)

# Assuming your data frame is named 'movies_with_air_condition'
# filter df first to see if the movie was actually able to be analysed.

# Define the ethnicities and counts for t1
ethnicities <- c("Black", "Asian", "Hispanic")
t1_counts <- c(
  sum(df$Total_Assigned_Black >= 2, na.rm = TRUE),
  sum(df$Total_Assigned_Asian >= 2, na.rm = TRUE),
  sum(df$Total_Assigned_Hispanic >= 2, na.rm = TRUE)
)

# Adding the named file

# Define the ethnicities and counts for t1 (for the named dataset)
t1_count_named <- c(
  sum(movies_simpson_named$Total_Assigned_Black >= 2, na.rm = TRUE),
  sum(movies_simpson_named$Total_Assigned_Asian >= 2, na.rm = TRUE),
  sum(movies_simpson_named$Total_Assigned_Hispanic >= 2, na.rm = TRUE)
)

# filter df first to see if the movie was actually able to be analyzed
df_filtered <- df %>%
  filter(imdb.com_imdbid %in% movies_with_air_condition$tt_number)

# Define the ethnicities and counts for t1 (for the filtered dataset)
t1_counts_filtered <- c(
  sum(df_filtered$Total_Assigned_Black >= 2, na.rm = TRUE),
  sum(df_filtered$Total_Assigned_Asian >= 2, na.rm = TRUE),
  sum(df_filtered$Total_Assigned_Hispanic >= 2, na.rm = TRUE)
)

#Initialize an empty data frame to store the results
result_df <- data.frame(Ethnicity = character(0), T1_Count_Named = numeric(0), T1_Count_All = numeric(0), T2_Count = numeric(0), T2_Count_named = numeric(0), T3_Count = numeric(0), T3_Count_named = numeric(0))

# Loop through each ethnicity
for (i in 1:length(ethnicities)) {
  ethnicity <- ethnicities[i]
  t1_count_named_ethnicity <- t1_count_named[i]
  t1_count_ethnicity <- t1_counts[i]
  t2_count <- sum(movies_with_air_condition[[paste0(ethnicity, "_condition_with_white_t2")]] == 1)
  t3_count <- sum(movies_with_air_condition[[paste0(ethnicity, "_condition_t3")]] == 1)
  t2_count_named <- sum(named_air_condit[[paste0(ethnicity, "_condition_t2")]] == 1)
  t3_count_named <- sum(named_air_condit[[paste0(ethnicity, "_condition_t3")]] == 1)

  # Add the counts to the result data frame
  result_df <- rbind(result_df, data.frame(Ethnicity = ethnicity, T1_Count_All = t1_count_ethnicity, T1_Count_Named = t1_count_named_ethnicity, T2_Count = t2_count, T2_Count_named = t2_count_named, T3_Count = t3_count, T3_Count_named = t3_count_named))
}

print(result_df)
```


# The second step would be to first filter the characters on 'named characters'and then run the same tests. 
```{r echo=FALSE}
result_df
result_df <- result_df %>%
  mutate(
    NC_T1 = sum(named_characters$Black >= 2, na.rm = TRUE) * (Ethnicity == "Black") +
            sum(named_characters$Asian >= 2, na.rm = TRUE) * (Ethnicity == "Asian") +
            sum(named_characters$Hispanic >= 2, na.rm = TRUE) * (Ethnicity == "Hispanic")
  )

print(result_df)

```


```{r echo = FALSE}
thanos_endgame <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos_endgame.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))

thanos_endgame <- left_join(thanos_endgame, named_air_condit, by = c("imdb.com_imdbid" = "tt_number"))

write.csv(thanos_endgame, "~/Master/Thesis/gen/data-preparation/output/thanos_endgame.csv")

```








# Paper doing name recognition https://aclanthology.org/N18-1200.pdf 

# Here we also would like to see if the results differ before and after 2016. Seeing if people from minoritiy groups gained more named character positions

```{r echo=FALSE}
thanos <- left_join(thanos, named_characters , by = c("imdb.com_imdbid" = "IMDb ID"))
```

```{r echo=FALSE}
# Categorize the data into "before 2015" and "after 2015"
thanos <- thanos %>%
  mutate(Category = ifelse(imdb.com_year < 2015, "Before 2015", "After 2015"))

# Calculate average counts exceeding 2 for "Black" and "Total_Assigned_Black" in each category
average_exceeding_2 <- thanos %>%
  group_by(Category) %>%
  summarise(
    Black = mean(Black[Black >= 2], na.rm = TRUE),
    Total_Assigned_Black = mean(Total_Assigned_Black[Total_Assigned_Black >= 2], na.rm = TRUE)
  )

# Reshape the data for plotting
average_long <- average_exceeding_2 %>%
  pivot_longer(cols = c(Black, Total_Assigned_Black),
               names_to = "Variable", 
               values_to = "Average_Count")

# Create the bar plot
ggplot(average_long, aes(x = Category, y = Average_Count, fill = Variable)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "Comparison of Average Counts Exceeding 2 (Black vs. Total_Assigned_Black)",
       x = "Category (Before 2015 vs. After 2015)") +
  theme_minimal()
```