---
title: "AIR exploration data"
author: "Bastiaan"
date: "2023-09-28"
output: html_document
---
```{r , load packages, echo=FALSE, message= FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyverse)
```

```{r echo=FALSE, message= FALSE, warning=FALSE}
named_air_condit <- read_csv("../../data/AIR_analysis/movies_with_air_condition_named.csv")

df <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos_endgame_done.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))

named_characters <- read_csv("../../data/AIR_analysis/named_characters.csv")

movies_simpson_named <- read_csv("../../gen/data-preparation/output/movies_simpson_named.csv")

movies_with_air_condition <- read_csv("../../data/AIR_analysis/movies_with_air_condition.csv")

```

# We started to do the anlysis midly. Here we just looked if there are more than 2 characters from the ethnicity. So they didn't neccesarly needed to be named. Here the scene index was 5 seconds for a new scene. T1 is from all the movies. Nevertheless, T2 and T3 are only from the movies which could be analysed. which were 1100. Moreover, we used people mentioned so there are most likely cases where someone is speaking about a person from the same ethncity group while they are actually not talking to that person. 

```{r echo=FALSE, message= FALSE, warning=FALSE}

df <- subset(df, imdb.com_imdbid %in% named_air_condit$tt_number)

movies_simpson_named_filtered <- subset(movies_simpson_named, Movie.ID %in% named_air_condit$tt_number)

# Assuming your data frame is named 'movies_with_air_condition'
# filter df first to see if the movie was actually able to be analysed.

# Define the ethnicities and counts for t1
ethnicities <- c("Black", "Asian", "Hispanic")
t1_counts <- c(
  sum(df$Total_Assigned_Black >= 2, na.rm = TRUE),
  sum(df$Total_Assigned_Asian >= 2, na.rm = TRUE),
  sum(df$Total_Assigned_Hispanic >= 2, na.rm = TRUE)
)

# Adding the named file

# Define the ethnicities and counts for t1 (for the named dataset)
t1_count_named <- c(
  sum(movies_simpson_named_filtered$Total_Assigned_Black >= 2, na.rm = TRUE),
  sum(movies_simpson_named_filtered$Total_Assigned_Asian >= 2, na.rm = TRUE),
  sum(movies_simpson_named_filtered$Total_Assigned_Hispanic >= 2, na.rm = TRUE)
)

#Initialize an empty data frame to store the results
result_df <- data.frame(Ethnicity = character(0), T1_Count_Named = numeric(0), T1_Count_All = numeric(0), T2_Count = numeric(0), T2_Count_named = numeric(0), T3_Count = numeric(0), T3_Count_named = numeric(0))

# Loop through each ethnicity
for (i in 1:length(ethnicities)) {
  ethnicity <- ethnicities[i]
  t1_count_named_ethnicity <- t1_count_named[i]
  t1_count_ethnicity <- t1_counts[i]
  t2_count <- sum(movies_with_air_condition[[paste0(ethnicity, "_condition_t2")]] == 1)
  t3_count <- sum(movies_with_air_condition[[paste0(ethnicity, "_condition_t3")]] == 1)
  t2_count_named <- sum(named_air_condit[[paste0(ethnicity, "_condition_t2")]] == 1)
  t3_count_named <- sum(named_air_condit[[paste0(ethnicity, "_condition_t3")]] == 1)

  # Add the counts to the result data frame
  result_df <- rbind(result_df, data.frame(Ethnicity = ethnicity, T1_Count_All = t1_count_ethnicity, T1_Count_Named = t1_count_named_ethnicity, T2_Count = t2_count, T2_Count_named = t2_count_named, T3_Count = t3_count, T3_Count_named = t3_count_named))
}

print(result_df)
```




```{r echo=FALSE, message= FALSE, warning=FALSE}
thanos_endgame <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos_endgame_done.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))



movies_simpson_named <- movies_simpson_named %>%
  mutate(
    black_t1 = ifelse(Total_Assigned_Black >= 2, 1, 0),
    hispanic_t1 = ifelse(Total_Assigned_Hispanic >= 2, 1, 0),
    asian_t1 = ifelse(Total_Assigned_Asian >= 2, 1, 0)
  )

# Assuming 'black_t1', 'hispanic_t1', and 'asian_t1' are the columns we want to add
columns_to_add <- c("black_t1", "hispanic_t1", "asian_t1")

# Left join only specific columns from movies_simpson_named to thanos_endgame
thanos_endgame <- left_join(
  thanos_endgame,
  movies_simpson_named %>% select(Movie.ID, all_of(columns_to_add)),
  by = c("imdb.com_imdbid" = "Movie.ID")
)


thanos_endgame <- left_join(thanos_endgame, named_air_condit, by = c("imdb.com_imdbid" = "tt_number"))


write.csv(thanos_endgame, "~/Master/Thesis/gen/data-preparation/output/thanos_endgame_air.csv")

```