---
title: "diff in diff study"
author: "Bastiaan"
date: "2023-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

```


```{r echo=FALSE }

# load packages
library(readr)
library(dplyr)
library(broom)
library(ggplot2)
library(car)
library(stargazer)
library(lubridate)
library(kableExtra)
library(corrplot)
library(lmtest)
library(sandwich)
library(tidyr)
library(openxlsx)



df <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos_endgame_air.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))

thanos <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))

movie_ranks <- read_csv("../../gen/data-preparation/output/movie_ranks.csv")


```


# We noticed that the rankings for the movies before 2000 were not that accurate 
```{r echo=FALSE}

df <- df %>%
  dplyr::select(-"imdb.com_releasedate")



#Left join thanos$imdb.com_releasedate to df 
df <- df %>%
  left_join(thanos %>% dplyr::select(imdb.com_imdbid, imdb.com_releasedate),
            by = c("imdb.com_imdbid" = "imdb.com_imdbid"))
  

df_clean <- df %>%
  filter(imdb.com_year >= 2000)

# Convert 'Date' column to a date format
movie_ranks$Date <- as.Date(movie_ranks$Date)

# Filter the dataset for dates after 2003
movie_ranks <- movie_ranks %>%
    filter(Date >= as.Date("2003-01-01"))



```

<sub> only possible explanation that top 250 or etc. is a very difficult to get to. The movies that have been published the more competitive it is to have a movie that keeps remaining popular.Therefore, it is logical that the movies that are newer are less popular after three years. Nevertheless, it is very difficult to explain why these movies popularity dropped so much after 2011.  
# This would be the regression of the main analysis
<sub> to achieve homoskedacity we did filter out the movies that were before 2000. But we did not filter out outliners.  

```{r echo=FALSE}
# Create new columns for each year from 2000 to 2019
for (year in 2000:2019) {
  col_name <- as.character(year)  # Convert the year to a character
  df_clean[col_name] <- ifelse(df_clean$imdb.com_year == year, 1, 0)
}

df_clean$Metascore <- as.numeric(df_clean$Metascore)

# Replace NA values with zero in specific columns
df_clean$Nominee <- ifelse(is.na(df_clean$Nominee), 0, df_clean$Nominee)
df_clean$Winner <- ifelse(is.na(df_clean$Winner), 0, df_clean$Winner)
df_clean$the_numbers_com_dirpower_rank <- ifelse(is.na(df_clean$the_numbers_com_dirpower_rank), 0, df_clean$the_numbers_com_dirpower_rank)

# Apply log transformation with small_constant
small_constant <- 1  # Define your small constant value

df_clean$log_Nominee <- log(df_clean$Nominee  + small_constant)
df_clean$log_Winner <- log(df_clean$Winner + small_constant)
df_clean$log_remake <- log(df_clean$imdb.com_remake * 100 + small_constant)
df_clean$log_dir_power <- log(df_clean$the_numbers_com_dirpower_rank * 100  + small_constant)
df_clean$log_metascore <- log(df_clean$Metascore + small_constant)
df_clean$log_starpower <-log(df_clean$Total_Star_Power * 100 + small_constant)
df_clean$log_MPAA <- log(df_clean$mpaa_numeric + small_constant)
df_clean$log_sequel <- log(df_clean$imdb.com_sequel + small_constant)


# Seasonality
# Create a new column for each season
df_clean$Spring <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(3, 4, 5), 1, 0)
df_clean$Summer <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(6, 7, 8), 1, 0)
df_clean$Fall <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(9, 10, 11), 1, 0)
df_clean$Winter <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(12, 1, 2), 1, 0)


```




# Going for the Diff in Diff analysis
<we first removed all ranks for the dates that were before the release of the movies 
```{r echo = FALSE}
df_clean$treatment <- ifelse(df_clean$t1 > 0.3627456, 1, 0)

movie_ranks <- movie_ranks %>%
    left_join(select(df_clean, imdb.com_imdbid, treatment), 
              by = c("Movie_ID" = "imdb.com_imdbid"))

```



< we are checking for a parallel trend> 

```{r echo = FALSE}
# Assuming your data frame is named movie_ranks

# Filter the data into treatment and control groups
treatment_group <- movie_ranks %>%
  filter(treatment == 1) %>%
  group_by(Date) %>%
  summarise(avg_rank = mean(Rank))


control_group <- movie_ranks %>%
  filter(treatment == 0) %>%
  group_by(Date) %>%
  summarise(avg_rank = mean(Rank))

```


```{r echo = FALSE}
# Create the plot
ggplot() +
  geom_line(data = treatment_group, aes(x = Date, y = avg_rank, color = "Treatment Group"), size = 1) +
  geom_line(data = control_group, aes(x = Date, y = avg_rank, color = "Control Group"), size = 1) +
  labs(title = "Average Ranking Over Time",
       x = "Date",
       y = "Average Ranking") +
  scale_color_manual(values = c("Treatment Group" = "gray", "Control Group" = "black")) +
  theme_minimal()
```

#running diff in diff normal movie ranks
```{r}
movie_ranks$time_indicator <- as.integer(movie_ranks$Date >= as.Date("2016-02-01"))

model_diff <- lm(Rank ~ treatment * time_indicator, data = movie_ranks)

summary(model_diff)

```


#running diff in diff movie ranks with t3
```{r}
df_clean_AIR <- df_clean[complete.cases(df_clean$Hispanic_condition_t2), ]

df_clean_AIR <- df_clean_AIR %>%
  mutate(imdb.com_releasedate = as.Date(imdb.com_releasedate),
         after_jan_2015 = as.numeric(imdb.com_releasedate > as.Date("2015-03-01")))

movie_ranks_AIR <- movie_ranks %>%
    filter(Movie_ID %in% df_clean_AIR$imdb.com_imdbid)


movie_ranks_AIR <- movie_ranks_AIR %>%
    left_join(select(df_clean_AIR, imdb.com_imdbid, Black_condition_t3, Asian_condition_t3, Hispanic_condition_t3), 
              by = c("Movie_ID" = "imdb.com_imdbid"))

    

model_diff_black <- lm(Rank ~ time_indicator * Black_condition_t3, data = movie_ranks_AIR)
model_diff_asian <- lm(Rank ~ time_indicator * Asian_condition_t3, data = movie_ranks_AIR)
model_diff_hisp<- lm(Rank ~ time_indicator * Hispanic_condition_t3, data = movie_ranks_AIR)

summary(model_diff_black)
summary(model_diff_asian)
summary(model_diff_hisp)

```


# running step dummy
```{r echo=FALSE}
df_clean <- df_clean %>%
  mutate(imdb.com_releasedate = as.Date(imdb.com_releasedate),
         after_jan_2015 = as.numeric(imdb.com_releasedate > as.Date("2015-03-01")))



# Create the main regression model
model_step <- lm(log(Avg_Rank_Third_Year) ~
                simpson_index * after_jan_2015  +
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log(mpaa_numeric) + 
                log(average_budget) + 
                imdb.com_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomic + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall +
                `2001` + `2002` + `2003` + `2004` + `2005` + `2006` + `2007` + `2008` + `2009` + `2010` + `2011` + `2012` + `2013` + `2014` + `2015` + `2016` + `2017` +`2018` + `2019`
               # Adding the year dummy variables to the model (excluding 2000)
                ,
            data = df_clean_AIR)


# print model 
summary(model_step)
```

# step path b T3
```{r echo=FALSE}
# Create the main regression model
model_step_b <- lm(log(Avg_Rank_Third_Year) ~
                Hispanic_condition_t3 * after_jan_2015 +
                Black_condition_t3 * after_jan_2015 +
                Asian_condition_t3 * after_jan_2015 +
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log(mpaa_numeric) + 
                log(average_budget) + 
                imdb.com_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomic + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall +
               # Adding the year dummy variables to the model (excluding 2000)
                `2001` + `2002` + `2003` + `2004` + `2005` + `2006` + `2007` + `2008` + `2009` + `2010` + `2011` + `2012` + `2013` + `2014` + `2015` + `2016` + `2017` + `2018` + `2019`,
            data = df_clean_AIR)



# print model 
summary(model_step_b)
```



# running step dummy with t1
```{r echo=FALSE}
# Create the main regression model
model_step_b_t1 <- lm(log(Avg_Rank_Third_Year) ~
                hispanic_t1 * after_jan_2015 +
                black_t1* after_jan_2015 +
                asian_t1 * after_jan_2015 +
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log(mpaa_numeric) + 
                log(average_budget) + 
                imdb.com_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomic + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall +
               # Adding the year dummy variables to the model (excluding 2000)
                `2001` + `2002` + `2003` + `2004` + `2005` + `2006` + `2007` + `2008` + `2009` + `2010` + `2011` + `2012` + `2013` + `2014` + `2015` + `2016` + `2017` + `2018` + `2019` ,
            data = df_clean_AIR)



# print model 
summary(model_step_b_t1)
```


# T2 
```{r echo=FALSE}
# Create the main regression model
model_step_b_t2 <- lm(log(Avg_Rank_Third_Year) ~
                Hispanic_condition_t2 * after_jan_2015 +
                Black_condition_t2 * after_jan_2015 +
                Asian_condition_t2 * after_jan_2015 +
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log(mpaa_numeric) + 
                log(average_budget) + 
                imdb.com_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomic + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall +
               # Adding the year dummy variables to the model (excluding 2000)
                `2001` + `2002` + `2003` + `2004` + `2005` + `2006` + `2007` + `2008` + `2009` + `2010` + `2011` + `2012` + `2013` + `2014` + `2015` + `2016` + `2017` + `2018` + `2019`,
            data = df_clean_AIR)



# print model 
summary(model_step_b_t2)
```

# comparison path B T1, T2 , T3 
```{r echo = FALSE}
# Get model summaries
model_summaries <- bind_rows(
  glance(model_step_b) %>% mutate(model = "model_step_b"),
  glance(model_step) %>% mutate(model = "model_step"),
  glance(model_step_b_t1) %>% mutate(model = "model_step_b_t1"),
  glance(model_step_b_t2) %>% mutate(model = "model_step_b_t2")  # Add model_step_b_t2
)

# Get model coefficients with significance
model_coefficients <- bind_rows(
  tidy(model_step) %>% mutate(model = "model_step"),
  tidy(model_step_b) %>% mutate(model = "model_step_b"),
  tidy(model_step_b_t1) %>% mutate(model = "model_step_b_t1"),  # Add model_step_b_t1_air
  tidy(model_step_b_t2) %>% mutate(model = "model_step_b_t2")  # Add model_step_b_t2
)

model_coefficients_with_stars <- model_coefficients %>%
  mutate(
    significance = case_when(
      p.value < 0.001 ~ '***',
      p.value < 0.01 ~ '**',
      p.value < 0.05 ~ '*',
      TRUE ~ ''  # If none of the above conditions are met
    ),
    estimate = round(estimate, 3)  # Rounding 'estimate' to 3 decimal places
  )

model_coefficients_with_stars <- model_coefficients_with_stars %>%
  mutate(
    combined_estimate = paste(estimate, significance, sep = " ") # Creating a new variable by concatenating 'estimate' and 'significance'
  )


model_coefficients_pivot <- model_coefficients_with_stars %>%
  select(-std.error, -statistic, -p.value, -estimate, -significance) %>%  # Remove unnecessary columns
  spread(key = model, value = combined_estimate)

library(openxlsx)

# Writing the model summaries to an Excel file using openxlsx
write.xlsx(model_coefficients_pivot, file = "../../model_coefficients_diff_diff.xlsx")



```



# running step dummy with t1 air 
```{r echo=FALSE}

df_2015 <- df_clean %>%
    filter(imdb.com_year >= 2016)
    

# Create the main regression model
model_step_b_t1 <- lm(log(Avg_Rank_Third_Year) ~
                hispanic_t1 * after_jan_2015 +
                black_t1* after_jan_2015 +
                asian_t1 * after_jan_2015 +
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log(mpaa_numeric) + 
                log(average_budget) + 
                imdb.com_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomic + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall +
               # Adding the year dummy variables to the model (excluding 2000)
                `2001` + `2002` + `2003` + `2004` + `2005` + `2006` + `2007` + `2008` + `2009` + `2010` + `2011` + `2012` + `2013` + `2014` + `2015` + `2016` + `2017` + `2018` + `2019` ,
            data = df_clean_AIR)



# print model 
summary(model_step_b_t1)
```


############### extra #################################


```{r echo=FALSE}
model_variables <- c(
  "Avg_Rank_Third_Year",
  "simpson_index",
  "log_simpson_index",
  "boxofficemojo.com_openingtheaters",
  "imdb.com_runtime",
  "log_MPAA",
  "average_budget",
  "log_sequel",
  "imdb.com_sequel",
  "imdb.com_spinoff",
  "log_remake",
  "imdb.com_basedonbook",
  "imdb.com_basedonbookseries",
  "imdb.com_basedonplay",
  "imdb.com_basedoncomic",
  "imdb.com_basedoncomicbook",
  "imdb.com_basedonnovel",
  "imdb.com_basedonshortstory",
  "log_Nominee",
  "log_Winner",
  "log_dir_power",
  "log_metascore",
  "log_starpower",
  "Action",
  "Adventure",
  "Comedy",
  "Fantasy",
  "Crime",
  "Drama",
  "Mystery",
  "Thriller",
  "Romance",
  "Sci.Fi",
  "Biography",
  "Sport",
  "War",
  "Family",
  "Musical",
  "History",
  "Horror",
  "Music",
  "Documentary",
  "Western",
  "Spring",
  "Summer",
  "Fall",
  "Winter",
  "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019"
)


movie_ranks_extra <- movie_ranks %>%
    left_join(select(df_clean, all_of(c("imdb.com_imdbid", model_variables))), 
              by = c("Movie_ID" = "imdb.com_imdbid"))




movie_ranks_extra$time_indicator <- as.integer(movie_ranks_extra$Date >= as.Date("2016-02-01"))

model_diff_extra <- lm(Rank ~ treatment * time_indicator+ 
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log_MPAA + 
                log(average_budget) + 
                imdb.com_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomic + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall +
               # Adding the year dummy variables to the model (excluding 2000)
                `2001` + `2002` + `2003` + `2004` + `2005` + `2006` + `2007` + `2008` + `2009` + `2010` + `2011` + `2012` + `2013` + `2014` + `2015` + `2016` + `2017` + `2018` + `2019`
            , data = movie_ranks_extra)

summary(model_diff_extra)

```


<there is a parallel trend but what happend in 200 to 2002? Therefore, we double checked the IMDB website on web.archive.org and looking at those dates thats when the platform became way more user friendly. The IMDB top 250 movie was for example also non existing by that time> 


# the coeffient is actually significant. Nevertheless, this includes the 'bad data'before 2003. Lets remove those data and run it again. 

```{r echo = FALSE}
filtered_movie_ranks$time_indicator <- as.integer(filtered_movie_ranks$Date >= as.Date("2015-02-01"))

model_diff_filtered <- lm(Rank ~ treatment * time_indicator, data = filtered_movie_ranks)

summary(model_diff_filtered)
```
# the results of this model mean that if we clean all movies that were released before 2003. we still get a significant result for the interaction. What is even more inresting and valuable that movies after 2015 are far less popular, movies in the treatmant group meaning they have higher than the average racial diversity are also less popular. But when we combine them they become more popular. So let's change a few things 

# Let's adjust the threshold for the treatment group. 
```{r}
df$hard_treatment <- ifelse(df$simpson_index > 0.4, 1, 0)

# Add the treatment variable and imdb.com_releasedate to movie_ranks
hard_treatment_movie_ranks <- movie_ranks %>%
  left_join(df %>% select(hard_treatment, imdb.com_imdbid, imdb.com_releasedate), 
            by = c("Movie_ID" = "imdb.com_imdbid"))


# Convert imdb.com_releasedate to Date format (if not already)
hard_treatment_movie_ranks <- hard_treatment_movie_ranks %>%
  mutate(imdb.com_releasedate = as.Date(imdb.com_releasedate))

# Filter the dataset to keep only observations where Date is after imdb.com_releasedate
hard_filtered_movie_ranks <- hard_treatment_movie_ranks %>%
  filter(Date >= imdb.com_releasedate)

hard_filtered_movie_ranks <- hard_filtered_movie_ranks %>%
  filter(imdb.com_releasedate > 2003)
```


```{r eacho=FALSE}
df_clean <- df_clean %>%
  mutate(asian_t1 = ifelse(Total_Assigned_Asian >= 2, 1, 0))

df_clean <- df_clean %>%
  mutate(black_t1 = ifelse(Total_Assigned_Black >= 2, 1, 0))

df_clean <- df_clean %>%
  mutate(hispanic_t1 = ifelse(Total_Assigned_Hispanic >= 2, 1, 0))
```

