---
title: "Visualization"
author: "Bastiaan"
date: "2023-09-20"
output: 
  html_document:
    latex_engine: xelatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

```


```{r echo=FALSE }

# load packages
library(readr)
library(dplyr)
library(broom)
library(ggplot2)
library(car)
library(stargazer)
library(lubridate)
library(kableExtra)
library(corrplot)
library(lmtest)
library(sandwich)



df <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos_endgame_air.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))

thanos <- read_csv("~/Master/Thesis/gen/data-preparation/output/thanos.csv", 
                           col_types = cols(imdb.com_releasedate = col_datetime(format = "%Y-%d-%m")))
```


# We noticed that the rankings for the movies before 2000 were not that accurate 
```{r echo=FALSE}

df <- df %>%
  dplyr::select(-"imdb.com_releasedate")



#Left join thanos$imdb.com_releasedate to df 
df <- df %>%
  left_join(thanos %>% dplyr::select(imdb.com_imdbid, imdb.com_releasedate),
            by = c("imdb.com_imdbid" = "imdb.com_imdbid"))
  

df_clean <- df %>%
  filter(imdb.com_year >= 2000)
```

<sub> only possible explanation that top 250 or etc. is a very difficult to get to. The movies that have been published the more competitive it is to have a movie that keeps remaining popular.Therefore, it is logical that the movies that are newer are less popular after three years. Nevertheless, it is very difficult to explain why these movies popularity dropped so much after 2011.  
# This would be the regression of the main analysis
<sub> to achieve homoskedacity we did filter out the movies that were before 2000. But we did not filter out outliners.  

```{r echo=FALSE}
# Create new columns for each year from 2000 to 2019
for (year in 2000:2019) {
  col_name <- as.character(year)  # Convert the year to a character
  df_clean[col_name] <- ifelse(df_clean$imdb.com_year == year, 1, 0)
}

df_clean$Metascore <- as.numeric(df_clean$Metascore)

# Replace NA values with zero in specific columns
df_clean$Nominee <- ifelse(is.na(df_clean$Nominee), 0, df_clean$Nominee)
df_clean$Winner <- ifelse(is.na(df_clean$Winner), 0, df_clean$Winner)
df_clean$the_numbers_com_dirpower_rank <- ifelse(is.na(df_clean$the_numbers_com_dirpower_rank), 0, df_clean$the_numbers_com_dirpower_rank)

# Apply log transformation with small_constant
small_constant <- 1  # Define your small constant value

df_clean$log_Nominee <- log(df_clean$Nominee  + small_constant)
df_clean$log_Winner <- log(df_clean$Winner + small_constant)
df_clean$log_remake <- log(df_clean$imdb.com_remake * 100 + small_constant)
df_clean$log_dir_power <- log(df_clean$the_numbers_com_dirpower_rank * 100  + small_constant)
df_clean$log_metascore <- log(df_clean$Metascore + small_constant)
df_clean$log_starpower <-log(df_clean$Total_Star_Power * 100 + small_constant)
df_clean$log_MPAA <- log(df_clean$mpaa_numeric + small_constant)
df_clean$log_sequel <- log(df_clean$imdb.com_sequel + small_constant)
df_clean$simpson_index <- df_clean$simpson_index * 100


# Seasonality
# Create a new column for each season
df_clean$Spring <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(3, 4, 5), 1, 0)
df_clean$Summer <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(6, 7, 8), 1, 0)
df_clean$Fall <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(9, 10, 11), 1, 0)
df_clean$Winter <- ifelse(month(df_clean$imdb.com_releasedate) %in% c(12, 1, 2), 1, 0)


```

```{r echo = FALSE}
df_clean <- df_clean %>%
  filter(!is.na(Avg_Rank_Third_Year)) %>%
    filter(!is.na(imdb.com_sequel)) %>%
    filter(!is.na(mpaa_numeric))



# List of continuous variables you want in the table
continuous_vars <- c(
  "Avg_Rank_Third_Year",
  "simpson_index",
  "boxofficemojo.com_openingtheaters",
  "imdb.com_runtime",
  "average_budget",
  "Nominee",
  "Winner",
  "the_numbers_com_dirpower_rank",
  "Total_Star_Power",
  "Metascore",
  "imdb.com_sequel",
  "mpaa_numeric",
  "imdb.com_remake"
)

# Create a function to calculate the statistics
calculate_statistics <- function(x) {
  N <- length(x)
  Mean <- mean(x)
  SD <- sd(x)
  Min <- min(x)
  Max <- max(x)
  return(c(N, Mean, SD, Min, Max))
}


# Calculate statistics for each variable
statistics_list <- lapply(df_clean[continuous_vars], calculate_statistics)

# Create a data frame for the table
table_data <- data.frame(
  Variable_Name = continuous_vars,
  N = sapply(statistics_list, "[[", 1),
  Mean = sapply(statistics_list, "[[", 2),
  SD = sapply(statistics_list, "[[", 3),
  Minimum = sapply(statistics_list, "[[", 4),
  Maximum = sapply(statistics_list, "[[", 5)
)


# Print the table using the `kable()` function
kable(table_data,
       align = c("c", "r", "r", "r", "r"),
       caption = "Descriptive Statistics for Continuous Variables",
       row.names = FALSE)

```

# descriptive stats dummy variables
```{r , echo=FALSE}

# Create a list of years, genres, and other dummy variables
years <- c("2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009",
          "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")

genres <- c("Action", "Adventure", "Comedy", "Fantasy", "Crime", "Drama", "Mystery", "Thriller",
           "Romance", "Sci.Fi", "Biography", "Sport", "War", "Family", "Musical", "History",
           "Horror", "Music", "Documentary", "Western")

other_dummy_vars <- c("Spring", "Summer", "Fall", "Winter",  "imdb.com_basedonbook",
  "imdb.com_basedonbookseries",
  "imdb.com_basedonplay",
  "imdb.com_basedoncomic",
  "imdb.com_basedoncomicbook",
  "imdb.com_basedonnovel",
  "imdb.com_basedonshortstory",
  "imdb.com_spinoff")


# Create empty data frames to store the results for each group
year_result <- data.frame(Variable_name = character(0), N = numeric(0), Percentage = numeric(0))
genre_result <- data.frame(Variable_name = character(0), N = numeric(0), Percentage = numeric(0))
other_dummy_result <- data.frame(Variable_name = character(0), N = numeric(0), Percentage = numeric(0))

# Calculate the frequency statistics and percentages for each group
total_observations <- nrow(df_clean)

for (variable in c(years, genres, other_dummy_vars)) {
    freq_table <- table(df_clean[[variable]])
    total_obs <- sum(df_clean[[variable]] == 1)
    
    if (variable %in% years) {
        year_result <- rbind(year_result, data.frame(
            Variable_name = variable,
            N = freq_table[2],  # Count for value 1 (assuming 1 is the second level)
            Percentage = (freq_table[2] / total_observations) * 100
        ))
    } else if (variable %in% genres) {
        genre_result <- rbind(genre_result, data.frame(
            Variable_name = variable,
            N = freq_table[2],
            Percentage = (freq_table[2] / total_observations) * 100
        ))
    } else if (variable %in% other_dummy_vars) {
        other_dummy_result <- rbind(other_dummy_result, data.frame(
            Variable_name = variable,
            N = freq_table[2],
            Percentage = (freq_table[2] / total_observations) * 100
        ))
    }
}

# Sort the data frames in descending order based on the "N" column
year_result <- year_result %>% arrange(desc(N))
genre_result <- genre_result %>% arrange(desc(N))
other_dummy_result <- other_dummy_result %>% arrange(desc(N))


# Print the results for each group in separate tables using kable
cat("Years\n")
kable(year_result, align = "c")
cat("\nGenres\n")
kable(genre_result, align = "c")
cat("\nOther Dummy Variables\n")
kable(other_dummy_result, align = "c")

```




```{r echo = FALSE}

model_variables <- c(
  "Avg_Rank_Third_Year",
  "simpson_index",
  "boxofficemojo.com_openingtheaters",
  "imdb.com_runtime",
  "log_MPAA",
  "average_budget",
  "log_sequel",
  "imdb.com_sequel",
  "imdb.com_spinoff",
  "log_remake",
  "imdb.com_basedonbook",
  "imdb.com_basedonbookseries",
  "imdb.com_basedonplay",
  "imdb.com_basedoncomicbook",
  "imdb.com_basedonnovel",
  "imdb.com_basedonshortstory",
  "log_Nominee",
  "log_Winner",
  "log_dir_power",
  "log_metascore",
  "log_starpower",
  "Action",
  "Adventure",
  "Comedy",
  "Fantasy",
  "Crime",
  "Drama",
  "Mystery",
  "Thriller",
  "Romance",
  "Sci.Fi",
  "Biography",
  "Sport",
  "War",
  "Family",
  "Musical",
  "History",
  "Horror",
  "Music",
  "Documentary",
  "Western",
  "Spring",
  "Summer",
  "Fall",
  "Winter",
  "2000", "2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019"
)

df_clean_subset <- df_clean[model_variables]

# Filter out rows with missing values in df_clean_subset
df_clean_subset <- df_clean_subset[complete.cases(df_clean_subset), ]


# Create the main regression model
model <- lm(log(Avg_Rank_Third_Year) ~ simpson_index +
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log_MPAA + 
                log(average_budget) + 
                log_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall +
               # Adding the year dummy variables to the model (excluding 2000)
                `2001` + `2002` + `2003` + `2004` + `2005` + `2006` + `2007` + `2008` + `2009` + `2010` + `2011` + `2012` + `2013` + `2014` + `2015` + `2016` + `2017` + `2018` + `2019`,
            data = df_clean)


# print model 
summary(model)


# Create a kable object for the table data
kable_table <- kable(table_data, format = "html") %>%
  kable_styling("striped", full_width = FALSE) %>%
  kable_classic(full_width = FALSE)

# Print the table
cat(kable_table)

```

# multicollinearity 
```{r echo=FALSE}

vif_value <- vif(model)
vif_value <- data.frame(VIF_Values = vif_value)


```


# colleration matrix
```{r echo=FALSE}
# Calculate the correlation matrix
cor_matrix <- cor(df_clean_subset)


# Print the correlation matrix
print(cor_matrix)

# Find rows and columns with correlation coefficients of 1 or -1
perfect_collinearity <- which(abs(cor_matrix) == 1, arr.ind = TRUE)

# Print the row and column names with perfect collinearity
for (i in 1:nrow(perfect_collinearity)) {
  row_idx <- perfect_collinearity[i, 1]
  col_idx <- perfect_collinearity[i, 2]
  row_name <- rownames(cor_matrix)[row_idx]
  col_name <- colnames(cor_matrix)[col_idx]
  cat("Perfect collinearity between", row_name, "and", col_name, "\n")
}
```


# Homoskedacity
```{r echo=FALSE}

# Extract the residuals from the model
residuals <- residuals(model)

# Generate a set of quantiles from a normal distribution with the same mean and standard deviation as the residuals
expected_quantiles <- qnorm(ppoints(length(residuals)), mean = mean(residuals), sd = sd(residuals))

# Create the P-P plot
plot(expected_quantiles, sort(residuals), xlab = "Expected Quantiles", ylab = "Observed Quantiles")
abline(0, 1, col = "red")


# Perform the White test for heteroskedasticity
white_test <- bptest(model)

# Print the White test results
print(white_test)

# Calculate robust standard errors
robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

# View the summary of your model
summary(model)

# Apply robust standard errors to the model coefficients
coeftest(model, vcov = vcovHC, type = "HC1")

# Extract the robust standard errors
robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

# Extract the model coefficients
model_coefs <- coef(model)

# Extract the p-values
p_values <- summary(model)$coefficients[, "Pr(>|t|)"]

# Create a function to format p-values
format_p_value <- function(p) {
  if (p < 0.001) {
    return(paste("< 0.001", "***"))
  } else {
    return(paste(signif(p, digits = 4), " "))
  }
}

# Apply the format_p_value function to the p-values
formatted_p_values <- sapply(p_values, format_p_value)

# Combine the coefficients, their robust standard errors, and p-values
coefs_se_pvalues <- data.frame(Coefficient = model_coefs, `Robust SE` = robust_se, `P-value` = formatted_p_values)

# Create a table using kable
kable(coefs_se_pvalues, format = "markdown")
```



```{r echo=FALSE}


stargazer(model, type = "text")

mytable <- stargazer(model, type = "text", out = "mytable.tex")
cat("\\input{mytable.tex}")

mt <- mtable(model)

write_html(mt, "mt.html")

```




# let's remove the year dummy variables 
```{r echo=FALSE}
# Create the main regression model
model_no_year <- lm(log(Avg_Rank_Third_Year) ~ simpson_index + 
                log(boxofficemojo.com_openingtheaters) + 
                log(imdb.com_runtime) + log_MPAA + 
                log(average_budget) + 
                log_sequel + 
                imdb.com_spinoff +
                log_remake +
                imdb.com_basedonbook + 
                imdb.com_basedonplay + 
                imdb.com_basedoncomic + 
                imdb.com_basedoncomicbook + 
                imdb.com_basedonnovel + 
                imdb.com_basedonshortstory + 
                log_Nominee +
                log_Winner +
                log_dir_power +
                log_metascore + 
                log_starpower +
                 # Include all genre variables
                Action + Adventure + Comedy + Fantasy + Crime + Drama + Mystery + Thriller + Romance + Sci.Fi + Biography + Sport + War + Family + Musical + History + Horror + Music + Documentary + Western +
            # including seasonality
                Spring +
                Summer +
                Fall,
            data = df_clean_subset)


# print model 
summary(model_no_year)
```
# Let's see if box office is related to average ranking 

```{r echo=FALSE}

df_clean$Box.Office <- as.numeric(df_clean$Box.Office)

model_box_office <- lm(Avg_Rank_Third_Year ~ Box.Office, data = df_clean)
model_box_office_year_1 <- lm(Avg_Rank_First_Year ~ Box.Office, data = df_clean)
model_rank_release <- lm(rank_release ~ Box.Office, data = df_clean)

# print model 
summary(model_box_office)
summary(model_box_office_year_1)
summary(model_rank_release)

# Scatterplot for model_box_office
ggplot(df, aes(x = Box.Office, y = Avg_Rank_Third_Year)) +
  geom_point() +                # Add points
  geom_smooth(method = "lm") +  # Add a linear regression line
  labs(
    x = "Box Office",
    y = "Avg Rank Third Year",
    title = "Scatterplot of Avg Rank Third Year vs. Box Office"
  )

```

# Let's first check the average ranking per year of the movies
```{R echo = FALSE}
ggplot(df_clean, aes(x = imdb.com_year, y = Avg_Rank_Third_Year)) +
  geom_line(stat = "summary", fun = "mean", fill = "skyblue") +
  labs(title = "Average Avg_Rank_Third_Year.y by imdb.com_year",
       x = "imdb.com_year",
       y = "Average Avg_Rank_Third_Year.y") +
  theme_minimal()

```
